COG-ED Manuscript

### 2021-08-19 06_Paper/COG-ED/Manuscript.Rmd
changed structure of SV data frame
To fit the ANOVA requirements of long data

  data_SV <- data.frame(subject = character(), sv1 = double(), sv2 = double(), sv3 = double(), sv4 = double())

@@

    newdata <- data.frame(data_ED$subject[subjectindex[i]], mean(tempone), mean(temptwo), mean(tempthree), mean(tempfour))
    colnames(newdata) <- names(data_SV)
    data_SV <- rbind(data_SV, newdata)

>>>>

  data_SV <- data.frame(subject = character(), level = double(), sv = double())

@@

    newdata <- data.frame(subject = rep(data_ED$subject[subjectindex[i]],4),
                          level = c(1:4),
                          sv = c(mean(tempone), mean(temptwo), mean(tempthree), mean(tempfour)))
    data_SV <- rbind(data_SV, newdata)
